---
title: "Untitled"
author: "Edwige"
date: "October 18, 2015"
output: html_document
---
```{r}
library(XML)
library(RCurl)
library(rjson)
library(RJSONIO)
library(jsonlite)
```

#Processing the HTML file
```{r}
#File location
url4html <-"https://raw.githubusercontent.com/fangseup88/Assignment_Week7/master/books.html"

#Getting the data file
file4html <- getURL(url4html)

#Create dataframe 
df4html <-  data.frame(readHTMLTable(file4html))
```

#Processing XML file
```{r}
url4xml <-"https://raw.githubusercontent.com/fangseup88/Assignment_Week7/master/books.xml"
#Getting the data file
file4xml <- getURL(url4xml)
#Create dataframe 
intermxml <- xmlTreeParse(file4xml)
df4xml<-data.frame(xmlToList(intermxml, addAttributes=FALSE))
```

#Processing JSON file
```{r}
#Location of the file
url4json <-"https://raw.githubusercontent.com/fangseup88/Assignment_Week7/master/books.json"
#Getting the data file
file4json <- getURL(url4json)
#Create dataframe 
df4json <- data.frame(fromJSON(file4json))

```

#Print the results
```{r}
#data frame for HTML
print(df4html)
#data frame for XML
print(df4xml)
#data frame for JSON
print(df4json)
```

#Conclusion
All the data frames contain the informations displayed  in the initial files. It is showing that the data frames for HTML and JSON have the same structure. In those datafiles, the informations about the books are mixed together. The data frame for XML is different, it follows the input file structure. 